\documentclass[12pt,a4paper]{article}
\usepackage{titlesec}
\usepackage{fancyhdr}

\usepackage[utf8]{inputenc}

\usepackage{graphicx}

\usepackage{booktabs}
\usepackage{array}
\usepackage{paralist}
\usepackage{verbatim}
\usepackage{subfig}
\usepackage[toc,page]{appendix}

\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\setlength{\headheight}{15pt}
\fancyhead[L]{Joe Bloggs - 2201882}
\fancyhead[R]{ SOC10101 Honers Project}
\fancyfoot[L]{}
\fancyfoot[C]{\thepage}

\makeatletter
\renewcommand\subsection{\@startsection {subsection}{1}{2mm}
                               {3pt plus 2pt minus 1pt}
                               {3pt plus 0pt}
                               {\normalfont\bfseries}}
\makeatother
\makeatletter
\renewcommand\section{\@startsection {section}{1}{0mm}
                               {4pt plus 2pt minus 1pt}
                               {4pt plus 0pt}
                               {\bfseries}}
\makeatother

\begin{document}

\input{./Dissertation-Title.tex}
\input{./Dissertation-Dec.tex}
\pagebreak
\input{./Dissertation-DP.tex}
\pagebreak

\begin{abstract}
\end{abstract}
\pagebreak

\tableofcontents
\newpage

\listoftables
\newpage

\listoffigures
\newpage

\section*{Acknowledgements}
Insert acknowledgements here
\subsection*{}
	I would like to thank my cat, dog and family.
\newpage


\section{Title of section would go here}
You can fill out sections as you please. \\

Most of the formatting is taken care for you but you can add this yourself as you please.

\subsection{Title of subsection would go here}
Or have sections that are relevant to your main body of work above but warrant there own section. Both - with numbering would be entered into the Table of contents.


 \subsubsection{Overview Of Project Content and Milestones}

This is a sub sub section with a list of bullet points.
\begin{itemize}\itemsep0pt
	\item A working X, that will be used for this investigation.
	\item Investigation of current tools and their potential use during an investigation of X .
	\item Programming of X with related frameworks Y and Z.
	\item That is all.
\end{itemize}


\section{Chapter 2}
And so on for each of the chapters.  The template automatically starts new chapters on a new page.  The associated guidelines tell you what the available styles do and also how to structure a report.
There is a section break on this page that you should be careful NOT to delete otherwise the references and appendices will be numbered continuously with the rest of the document.

\section{Additional Information / Knowledge Required}
Experience with Linux and managing Virtual machines, networking.
So on and so forth...

\newpage
\begin{thebibliography}{9}

\bibitem{lamport94}
  Leslie Lamport,
  \emph{\LaTeX: A Document Preparation System}.
  Addison Wesley, Massachusetts,
  2nd Edition,
  1994.

\end{thebibliography}
\newpage
\begin{appendices}
\section{Project Overview}

\begin{subappendices}
\subsection{Example sub appendices}
...
\end{subappendices}

\section{Second Formal Review Output}
Insert a copy of the project review form you were given at the end of the review by the second marker

\section{Diary Sheets (or other project management evidence)}
Insert diary sheets here together with any project management plan you have

\section{Appendix 4 and following}
insert content here and for each of the other appendices, the title may be just on a page by itself, the pages of the appendices are not numbered, unless an included document such as a user manual or design document is itself pager numbered.
\end{appendices}

\end{document}
